---
title: "Annual Business Survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Annual Business Survey 

The Census released the [Annual Business Survey](https://www.census.gov/programs-surveys/abs.html) in 2018. This survey collects important information about the demographics of business owners across the United States. They've only released information covering 2017, but I think there's a way to link that information with the older [Survey of Business Owners](https://www.census.gov/programs-surveys/sbo.html), so stay tuned once I learn how to do that.

![ABO Homepage](static/img/abs_screenshot)

## Downloading the Data 

The Census website is not the most user friendly (at least to me), and they got rid of the American fact-finder site. Since this is just onw table, we can just [go to the data page](https://www.census.gov/programs-surveys/abs/data.html) and download the table. There's also documentation to build your own API to pull the data in directly.  Let's give it a shot!

```{r, echo=FALSE}
library(dplyr)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
